openarchaeoCollaboration

### 2021-06-13 analysis/paper.Rmd
Expand lifespan/activity analysis

TODO: barcode plot (see above)

>>>>

```{r lifespan-stats}
oarch %>% 
  unnest(gh_commits) %>% 
  drop_na(datetime) %>% 
  group_by(item_name) %>%
  summarise(
    n = n(),
    first_commit = min(datetime),
    last_commit = max(datetime),
    lifespan = as.integer(last_commit - first_commit),
    commit_rate = n / lifespan
  ) ->
  oarch_lifespan
```

```{r plot-lifespan-hist}
oarch_lifespan %>% 
  ggplot(aes(x = lifespan)) +
  geom_histogram() +
  labs(
    title = "Project lifespan",
    subtitle = "Time between first and latest commit",
    x = "Days", y = "Repositories",
    caption = "Data: open-archaeo.info and GitHub API"
  )
```
```{r plot-rate-hist}
oarch_lifespan %>% 
  ggplot(aes(x = commit_rate)) +
  geom_histogram() +
  labs(
    title = "Project activity",
    subtitle = "Average commit rate",
    x = "Commits per day", y = "Repositories",
    caption = "Data: open-archaeo.info and GitHub API"
  )
```

What are the characteristics of long-lived and/or active repositories?

```{r plot-lifespan-vs-rate}
oarch_lifespan %>% 
  ggplot(aes(x = lifespan, y = commit_rate)) +
  geom_point() +
  scale_x_log10() +
  scale_y_log10() +
  labs(
    title = "Project lifespan vs. average commit rate",
    x = "Lifespan (days)", y = "Commits per day",
    caption = "Data: open-archaeo.info and GitHub API"
  )
```

TODO: ZB: Any ideas for other relevant factors? Lots of ways you could go here...
